\LARGE \bf Simultaneous Coordinate Calibrations by Solving the AX=YB Problem without Correspondence*

### 2015-06-19 Tex_AXYB/paper.tex
need to be revised

%% This skeleton file requires IEEEtran.cls version 1.6 or later.
%%
\documentclass[conference,letterpaper]{IEEEtran}
% If the IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it:
% \documentclass[conference]{../sty/IEEEtran}
\IEEEoverridecommandlockouts
\overrideIEEEmargins

% some very useful LaTeX packages include:

\usepackage{cite}      % Written by Donald Arseneau
                        % V1.6 and later of IEEEtran pre-defines the format
                        % of the cite.sty package \cite{} output to follow
                        % that of IEEE. Loading the cite package will
                        % result in citation numbers being automatically
                        % sorted and properly "ranged". i.e.,
                        % [1], [9], [2], [7], [5], [6]
                        % (without using cite.sty)
                        % will become:
                        % [1], [2], [5]--[7], [9] (using cite.sty)
                        % cite.sty's \cite will automatically add leading
                        % space, if needed. Use cite.sty's noadjust option
                        % (cite.sty V3.8 and later) if you want to turn this
                        % off. cite.sty is already installed on most LaTeX
                        % systems. The latest version can be obtained at:
                        % http://www.ctan.org/tex-archive/macros/latex/contrib/supported/cite/

@@

%\usepackage{amsmath}   % From the American Mathematical Society
                        % A popular package that provides many helpful commands
                        % for dealing with mathematics. Note that the AMSmath
                        % package sets \interdisplaylinepenalty to 10000 thus
                        % preventing page breaks from occurring within multiline
                        % equations. Use:
\usepackage{multirow}
\usepackage[left=0.71in,top=0.94in,right=0.71in,bottom=1.18in]{geometry}
\setlength{\columnsep}{0.24in}
% correct bad hyphenation here
%\hyphenation{op-tical net-works semi-conduc-tor IEEEtran}

\begin{document}
% paper title
\title{\huge Simultaneous Coordinate Calibrations by Solving the AX=YB Problem without Correspondence $^{*}$\footnoterule\thanks{$^{*}$This work is partially
supported by NSF Grant RI-Medium: \#IIS-1162095 to }}

% author names and affiliations
\author{\authorblockN{Haiyuan Li}
\authorblockA{\textit{School of Mechanical Engineering}\\
\textit{Beihang University}\\
\textit{Beijing, China}\\
\textit{lihaiyuan@buaa.edu.cn}\\}%
\and
\authorblockN{Gregory S. Chirikjian}
\authorblockA{\textit{Department of Intelligent Robotics}\\
\textit{Johns Hopkins University}\\
\textit{Baltimore, Maryland, USA}\\
\textit{gregc@jhu.edu}\\}}%

% make the title area
\maketitle
\begin{abstract}

\\
\end{abstract}

% key words
\begin{keywords}
AX=YB, Sensor Calibration, Probabilistic Modeling
\end{keywords}

@@

Image-guided system has been widely used in robotics such as robot assisted surgery. Sensors such as a camera, a laser scanner and an ultrasound probe are usually mounted as the end-effector of a robotic manipulator. For a typical ``hand-eye" system as described above, the relative transformation of the sensor with respect to the end-effector should be accurately calibrated, and it is often characterized as the well known $\textbf{AX=XB}$ problem. A variation of this problem is characterized as the $\textbf{AX=YB}$ problem, where both the hand-eye transformation and the pose of the robot base with respect to the world frame need to be calibrated. In a typical environment setup, the relationship among the sensor frame, robot frame and world frame either is subject to change or can be disturbed by uncertainties. Therefore, simultaneous coordinate calibrations have to be performed frequently in order to enable the robot to respond to dynamic environments.

In the $\textbf{AX=YB}$ problem, $A$s and $B$s can be respectively obtained via different sensors. The data streams can be in an asynchronous fashion due to different working frequencies of the sensors. The asynchrony causes a shift between the two streams of data which damages the correspondence between $A$s and $B$s. In this paper, we present a method to solve for $X$ and $Y$ without the need to know a priori knowledge of the correspondence between $A$s and $B$s.

\begin{center}
\begin{figure}[htbp]
\centering
\includegraphics[width=2in]{fig1.eps}
\caption{
(1) The hand-eye calibration problem formulated in a matrix as AX=XB. (2) The hand-eye and robot-robot calibration problem formulated as AX=YB.
}
\label{fig1}
\end{figure}
\end{center}

The hand-eye calibration problem can be modeled as the $\textbf{AX = XB}$, where $A$s and $B$s are the homogeneous transformation matrices describing the relative motion of the end-effector and the sensor respectively. As shown in Fig.~\ref{fig1}, $A_{i} = A^{i}(A^{i+1})^{-1}$ and $B_{i} = B^{i}(B^{i+1})^{-1}$. The homogeneous transformation matrix can be described as:
\begin{equation}\label{equ0}
    g(R,t)=\left(
             \begin{array}{cc}
               R & t \\
               0^{T} & 1 \\
             \end{array}
           \right)
\end{equation}

@@

Given multiple pairs of $\{A_{i},B_{i}\} \in SE(3) \times SE(3)$ with correspondence, many methods have been proposed to solve for $X$. To the best of the authors' knowledge, Shiu\cite{Shiu1989} and Tsai\cite{Tsai1989} are the first to solve the $AX=XB$ sensor calibration problem. The other methods include but are not limited to quaternion, dual quaternion, screw theory, Lie group theory, convex optimization and gradient descent methods \cite{Wang1992,Park1994,Horaud1995,Daniilidis1999,Fassi2005,Zhao2011,Ackerman2014a}. All of the methods above assume a prior knowledge of exact correspondence  between $A_{i}$ and $B_{i}$. For data streams $\{A_{i}\}$ and $\{B_{j}\}$ that are asynchronous, several methods have been proposed in the literature to solve for $X$ using data without correspondence \cite{Ackerman2013a,Ackerman2013,Ackerman2014}.

Simultaneous estimation of the hand-eye and robot-world transformations
has been viewed as the $\textbf{AX=YB}$ problem. As shown in Fig.\ref{fig1}, $Y$ is the transformation of the robot base relative to the world frame, $A$ denotes the sensor's pose in the world frame, and $B$ is the transformation of  the end-effector with respect to its fixed base. The $A_{i}$ and $B_{i}$ in $\textbf{AX=YB}$ are different from those in $\textbf{AX=XB}$ which can be seen in Fig.\ref{fig1}. The $\textbf{AX=YB}$ problem has been solved by different methods such as kronecker product, quaternion, dual quaternion, and nonlinear optimization method \cite{Zhuang1994,dornaika1998simultaneous,Hirsh2001, ernst2012non,strobl2006optimal,Li2010,Shah2013,Heller2014}. Simultaneous calibration of $X$ and $Y$ can be problematic in that all the methods above assume exact correspondence between $\{A_{i}\}$ and $\{B_{j}\}$, which is not the case in real experiments. Another similar problem involves the calibration of multiple robots in terms of hand-eye, tool-flange and robot-robot system, and it is formulated as the $\textbf{AXB=YCZ}$ problem \cite{Wang2014}. In this paper, we focus on the $\textbf{AX=YB}$ problem which does not require a priori knowledge of correspondences of the data streams.

The rest of the paper is organized as follows. In Section
\ref{sect2}, we present a probabilistic method to solve for $X$ and $Y$. In Section \ref{sect3}, a algorithmic solution involving both the correlation theorem and Euclidean group invariants is posed to recover the correspondence between $\{A_{i}\}$ and $\{B_{j}\}$. The simulation results which deal with the data streams with both known and unknown correspondence are illustrated in Section \ref{sect4}. Finally, conclusions are drawn based on the numerical results and possible future works are pointed out.

@@

Given a large set of pairs $\{A_{i},B_{i}\}\in SE(3)\times SE(3)$ for $i=1,\cdots,n$ that are acquired by measurements and satisfy the following equation:
\begin{equation}\label{equ1}
A_{i}X=YB_{i}.
\end{equation}
For a matrix $H \in SE(3)$, a Dirac delta function $\delta(H)$ function is defined to be finite only at the identity and zero everywhere else:

\begin{equation}\label{equ2}
\delta{(H)}=
\left\{
\begin{array}{ll}
+\infty, & H=I \\
0, & H \neq I
\end{array}
\right.
\end{equation}
It also satisfies the identity constraint as:
\begin{equation}\label{equ3}
\int_{SE(3)}\delta{(H)}dH=1.
\end{equation}

A shifted Dirac delta function can be defined as $\delta_{A}(H)=\delta{(A^{-1}H)}$. Given $K, H \in SE(3)$ and two functions $f_1, f_2 \in (L^1 \cap L^2)(SE(3))$, their convolution on $SE(3)$ is defined as:

\begin{equation}\label{equ4}
(f_{1}\ast f_{2})(H)=\int_{SE(3)}f_{1}(K)f_{2}(K^{-1}H)dK
\end{equation}
where $h \in SE(3)$. Employing the properties of $\delta$ function, it is straightforward to see that:

\begin{equation}\label{equ5}
(f\ast \delta)(H)=\int_{SE(3)}f(K)\delta(K^{-1}H)dK=f(H).
\end{equation}
Therefore, for each $A_{i}$ and $B_{i}$, we have:

\begin{IEEEeqnarray}{l}\label{equ6}
(\delta_{A_{i}}\ast \delta_{X})(H)=\delta(A_{i}^{-1} H X^{-1}) \IEEEyessubnumber
\\*
(\delta_{Y}\ast \delta_{B_{i}})(H)=\delta(Y^{-1} H B_{i}^{-1}) \IEEEyessubnumber
\end{IEEEeqnarray}
Together with $A_{i}X=YB_{i}$, we can obtain the convolution equation:

\begin{equation}\label{equ7}
(\delta_{A_{i}}\ast \delta_{X})(H)=(\delta_{Y}\ast \delta_{B_{i}})(H)
\end{equation}

Convolution provides a linear operation on functions with addition properties.  After adding up $n$ instances of $\delta_{A_{i}}(H)$ and $\delta_{B_{i}}(H)$, we obtained the following equations:

\begin{IEEEeqnarray}{l}\label{equ8}
f_{A}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta(A_{i}^{-1}H) \IEEEyessubnumber
\\*
f_{B}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta(B_{i}^{-1}H) \IEEEyessubnumber
\end{IEEEeqnarray}

Therefore, we have:
\begin{equation}\label{equ9}
(f_{A}\ast \delta_{X})(H)=(\delta_{Y}\ast f_{B})(H).
\end{equation}

For each of the data stream $\{A_i\}$ and $\{B_i\}$, we are using small relative motions between consecutive reference frames. Take $\{A_{i}\}$ for example, one metric of the distance between $A_i$ and $A_j$ can be defined as:

\begin{eqnarray}\label{equ10}
d^{2}(A_{i},A_{i+1})=\parallel \Delta A \parallel_{W}^{2} = trace[(\Delta A)W(\Delta A)^{T}] = \epsilon,\nonumber \\
\end{eqnarray}
where  $\Delta A = A_{i}-A_{j}$ (or $\Delta A = A_{i}^{-1}A_{j}$) and $0 < \epsilon \ll 1 $

The convolution of two ``highly focused" probability density functions (pdf) has some interesting properties that can be used to solve for $X$. In particular, firstly, define the mean $M$ and covariance $\Sigma$ of a probability density function on $SE(3)$ as:

\begin{IEEEeqnarray}{l}\label{equ11}
\int_{SE(3)}log(M^{-1}H))f(H)dH=0 \IEEEyessubnumber
\\*
\Sigma = 
\int_{SE(3)}log^{\vee}(M^{-1}H)[log^{\vee}(M^{-1}H)]^{T}f(H)dH \IEEEyessubnumber
\end{IEEEeqnarray}

Then the corresponding discrete version of $f_{A}(H)$ will be:

\begin{IEEEeqnarray}{l}\label{equ12}
\sum_{i=1}^{n}log(M_{A}^{-1}H))=0 \IEEEyessubnumber
\\*
\Sigma_{A} = \sum_{i=1}^{n}log^{\vee}(M_{A}^{-1}H)[log^{\vee}(M_{A}^{-1)}H)]^{T} \IEEEyessubnumber
\end{IEEEeqnarray}

@@

An initial estimate of the iterative procedure can be $^{0}M_{A}=\frac{1}{n}\sum_{i=1}^{n}log(A_{i})$,then the process iterates until the cost function, $\parallel \sum_{i=1}^{n}log(M_{A}^{-1}A_{i}) \parallel^{2}$ falls below a predefined threshold, where the cost function is minimized and the minimum defines $M_{A}$. A similar procedure is used for computing $M_B$.

@@

Due to $X$ and $Y$ is fixed, as for $\delta_{X}(g)$ and $\delta_{Y}(g)$, mean and covariance are $M_{X}=X$,$\Sigma_{X}=0$ and $M_{Y}=Y$,$\Sigma_{Y}=0$, respectively, therefore we can obtain

@@

The first blocks(\ref{equ17a}) is eigendecomposed with the same diagonal matrix due to matrix similarity $\Sigma_{M_{A}}^{1}=Q_{M_{A}}\wedge Q_{M_{A}}^{T}$, $\Sigma_{M_{B}}^{1}=Q_{M_{B}}\wedge Q_{M_{B}}^{T}$. Then,

@@

In $P=Q_{M_{A}}^{T}R_{X}Q_{M_{B}}$, $Q_{M_{A}}$ and $Q_{M_{B}}$ are constrained to be a rotation matrix and therefore $P \in \Omega$,

@@

Therefore, there are four possibilities of $R_{X}, R_{X}=Q_{M_{A}}PQ_{M_{B}}^T$. Then, from \ref{equ17b},four $t_{X}$ corresponding to $R_{X}$ can be directly found. Furthermore,four candidate $R_{Y} and t_{Y}$ can be found. At last, there are four possibilities of solution $(X_{i},Y_{i}), i = 1,2,3,4$.
where,

@@

$AX=YB$ can be written as $AX=X(X^{-1}YB)$ and let $B' = X^{-1}YB$ . In the form $AX=XB'$, there exit two Euclidean-Group Invariant relationships for one of four groups of $(A_{i},B_{i}^k)( i = 1,\cdots,n; k=1,2,3,4)$ as follows,

@@

From among the four pairs $(X_{i},Y_{i})$, we can find a correct solution to minimize the leat absolute deviations,

@@

In most cases, the homogeneous transformations with $A$ and $B$ are given based on the data from different sensors. Due to asynchronous timing of the measurement transmissions, the correspondences between $A_{i}$ and $B_{i}^{k}$ is unknown. The advantage of the above probabilistic solution lie that $X$ and $Y$ can be calculated even if without any a priori knowledge of the correspondence. However, there are still four possible candidate results $(X_{i},Y_{i})$. Using Euclidean-Group Invariants, it is straightforward to determine which pair is the correct one if the correspondence between $A_{i}$ and $B_{i}^{k}$   can be known.

The Discrete Fourier transform (DFT) decomposes a time-domain signal into its constituent frequencies. The input is a finite list of equally spaced samples of a function. Given a discrete signal consisting of a sequence of $N$ complex numbers $x_{0},x_{1},\cdots,x_{N_1}$, the DFT is denoted by $X_{\kappa} = \mathcal{F}{x_{n}}$

\begin{equation}\label{equ21}
    X_{\kappa} = \sum_{n=0}^{N-1}x_{n}\cdot exp(-i\frac{2\pi}{N}n\kappa)
\end{equation}
And the Inverse Discrete Fourier transform (IDFT) denoted by

\begin{equation}\label{equ22}
    X_{n} = \frac{1}{N}\sum_{n=0}^{N-1}X_{\kappa}\cdot exp(i\frac{2\pi}{N}n\kappa)
\end{equation}

@@

Therefore, the correspondence between the two sequences can be found. The data of $\theta_{A_{i}}$ or $d_{A_{i}}$ are shifted by $-\tau_{shift}$ to obtain a sequence of new pairs $(\theta_{A_{i}}(i+\tau_{shift}),\theta_{B_{i}^{k}})$ and $(d_{A_{i}}(i+\tau_{shift}),d_{B_{i}^{k}})$, $max(i,i+\tau_{shift})\leq i \leq min(i,i+\tau_{shift})$. The data stream can be shifted to reach correspondence once the shift is found and the correct solution can also be found by minimizing the least absolute deviations based on Euclidean-Group Invariants relations using the method in Section \ref{sect2}.

@@

In the numerical experiments in this section, a homogeneous matrix   is generated from a PUMA 560 robotic manipulator. $X$ and $Y$ are chosen from reference .

\subsection{Results of solution with known correspondence}

100 pose measurements with $B_{i}$ closely around $B_{start}$ was employed for generating 100 $A_{i}$. As a result by applying the above probabilistic method, four sequences $(\theta_{A_{i}},\theta_{B_{i}^{k}})$ and $(d_{A_{i}},d_{B_{i}^{k}})$ $ (i=1,\cdots, 100, k=1,2,3,4)$ can be obtained respectively, as shown in Fig.~\ref{fig2} and Fig.~\ref{fig3}. Using $\theta_{A_{i}} - \theta_{B_{i}^{k}}$ and $d_{A_{i}} - d_{B_{i}^{k}}$  in Fig.~\ref{fig4} and Fig.~\ref{fig5}, we can find the ${B_{i}^{k}}(k=3)$  corresponding to the least sum of errors and then, $(X_3,Y_3)$ is the desired solution.

From 1 measurements to 500 measurements, the rotational and translational error for $X$ and $Y$ are measured as  $\parallel log^{\vee} (R_{X_{Solved}}^{T}R_{X_{true}})\parallel$, $\parallel (t_{X_{Solved}}-t_{X_{true}})\parallel$, $\parallel log^{\vee} (R_{Y_{Solved}}^{T}R_{Y_{true}})\parallel$ and $\parallel (t_{Y_{Solved}}-t_{Y_{true}})\parallel$ respectively as shown in Fig.~\ref{fig6}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if
                                                          % you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

@@

%\usepackage{amsmath}   % From the American Mathematical Society
                        % A popular package that provides many helpful commands
                        % for dealing with mathematics. Note that the AMSmath
                        % package sets \interdisplaylinepenalty to 10000 thus
                        % preventing page breaks from occurring within multiline
                        % equations. Use:
\usepackage{multirow}
%\usepackage[left=0.71in,top=0.94in,right=0.71in,bottom=1.18in]{geometry}
%\setlength{\columnsep}{0.24in}
% correct bad hyphenation here
%\hyphenation{op-tical net-works semi-conduc-tor IEEEtran}

\title{\LARGE \bf
Simultaneous Coordinate Calibrations by Solving the AX=YB Problem without Correspondence*
}

\author{Haiyuan Li$^{1}$, Qianli Ma$^{2}$, Tianmiao Wang$^{1}$ and Gregory Chirikjian$^{2}*$% <-this % stops a space
\thanks{*This work is partially
supported by NSF Grant RI-Medium: \#IIS-1162095}% <-this % stops a space
\thanks{$^{1}$Haiyuan Li and Tianmiao Wang is with the School of Mechanical Engineering and Automation, Beihang University,
        ,Beijing 100191, China
        {\tt\small lihaiyuan@buaa.edu.cn}}%
\thanks{$^{2}$Qianli Ma and Gregory Chirikjian with the Department of Mechanical Engineering, Johns Hopkins University,
        Baltimore, MD 21218, USA
        {\tt\small gregc@jhu.edu}}%
}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

In image-guided system, relationships of hand-eye ($X$) and robot-world ($Y$) coordinates have to be calculated and simultaneous solution is useful in sensor calibration problem. Due to asynchrony of sensors timing, the correspondence between $A$ and $B$ is unknown. A probabilistic method is presented to solve the
homogeneous matrix equations without a priori knowledge of the correspondence. Using Euclidean-Group invariants, an exact solution can be found. We illustrate the calculation in numeric simulation including various numbers of
robot movements. The results show the efficiency and robustness of the proposed simultaneous
method.

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Image-guided system has been widely used in robotics such as robot assisted surgery. A sensor such as camera, laser scanner or ultrasound probe is usually mounted on the hand of a robotic manipulator. To use the "hand-eye" system, the problem of determining the coordination relationship between the sensor frame with respect to the end-effector frame must be solved, which is widely known $\textbf{AX=XB}$ problem for the hand-eye calibration. With an extension of this problem, $\textbf{AX=YB}$ problem without knowing the relationship between the world frame and the robot base frame is proposed to achieve the robot-world calibration as well as hand-eye calibration. In a dynamic setup environment, the relationship among the sensor frame, robot frame and world frame is variant and the uncertainties exist. Therefore, simultaneous coordinate calibrations have to be determined frequently in order to enable the robots to respond to changing environments.

In the $\textbf{AX=YB}$ problem, $As$ and $Bs$ can be respectively calculated using different sensors. The data streams are in an asynchronous fashion due to different timing sequences. The asynchrony causes a shift between the two streams of data that results in missing the correspondences between $As$ and $Bs$. In this paper, we present a method to solve for an $X$ and $Y$ without needing know a priori knowledge of correspondence between $As$ and $Bs$.

\begin{center}
\begin{figure}[htbp]
\centering
\includegraphics[width=3.2in]{fig1.eps}
\caption{
(1) The hand-eye and robot-robot calibration problem which is formulated as AX=YB. (2) The hand-eye calibration problem which is formulated in a matrix as AX=XB.
}
\label{fig1}
\end{figure}
\end{center}

The hand-eye calibration problem can be generalized as the $\textbf{AX = XB}$ formulation. $A$ and $B$ are respectively the homogeneous transformation matrices of end-effector and sensor movement using $A = A^{i}(A^{i+1})^{-1}; B = B^{i}(B^{i+1})^{-1}$ as shown in Fig.~\ref{fig1}. The homogeneous transformation matrix can be described with the form.
\begin{equation}\label{equ0}
    g(R,t)=\left(
             \begin{array}{cc}
               R & t \\
               0^{T} & 1 \\
             \end{array}
           \right)
\end{equation}

@@

According to multiple pairs $(A,B) \in SE(3) \times SE(3)$ which are known a prior, many methods for the only $X$ have been proposed including decoupling of rotation and translation, least squares fitting, singular value decomposition (\emph{SVD}), screw theory, nonlinear
optimization, quaternion, gradient descent and interactive approaches \cite{Shiu1989,Tsai1989,Wang1992,Park1994,Horaud1995,Daniilidis1999,Fassi2005,Zhao2011,Ackerman2014a}. Theses methods assume that there is exact knowledge of the $As$ and $Bs$ correspondence. Considering data streams containing the $A$ and $B$ will be asynchronous that are discussed in many instances
in the literature, several methods regardless of the correspondence or recovering the correspondence between two data sets are presented \cite{Ackerman2013a,Ackerman2013,Ackerman2014}.

Simultaneous estimation of the hand-eye transformation and robot-world one
has been viewed as $\textbf{AX=YB}$ problem. As shown in Fig.~\ref{fig1} (1), $Y$ is the transformation of the robot base relative to the world, $A$ is the sensor to the world transformation, and $B$ is the hand/end-effector to the robot base rigid transformation. The $A$ and $B$ in $\textbf{AX=YB}$ calibration is different from ones in $\textbf{AX=XB}$ from a physical view. This problem has been studied in different methods such as SVD, closed-form, quaternion and nonlinear optimization \cite{Zhuang1994,dornaika1998simultaneous,Hirsh2001, ernst2012non,strobl2006optimal,Li2010,Shah2013,Heller2014}. Another approach integrate multiple robots to calibrate hand-eye, tool-flange and robot-robot transformation in $\textbf{AXB=YCZ}$ problem \cite{Wang2014}. Simultaneous solution for $X$ and $Y$ in $\textbf{AX=YB}$ problem is an challenging issue. In the above methods, the correspondence between $A$ and $B$ is known a prior. In this paper, our solution for $\textbf{AX=YB}$ doesn't require a priori knowledge of correspondences.

The rest of the paper is organized as follows. In Section
\ref{sect2} we present the probabilistic theory to solve for $X$ and $Y$. In Section \ref{sect3} a algorithmic solution involving correlation theorem and Euclidean group invariants is posed to recover the correspondence. The simulation results, including unknown correspondence and noisy data stream, are illustrated in Section \ref{sect4}. Finally, we draw some conclusions.

@@

Given a large set of pairs $(A_{i},B_{i})\in SE(3)\times SE(3)$ for $i=1,\cdots,n$ that are acquired by measurements and satisfy the following equations

\begin{equation}\label{equ1}
A_{i}X=YB_{i}
\end{equation}

In the case of $SE(3)$, a Dirac delta function, or $\delta$ function, is thought of as a function which is zero everywhere except at the identity where it is infinite.

\begin{equation}\label{equ2}
\delta{(H)}=
\left\{
\begin{array}{ll}
+\infty, & H=I \\
0, & H \neq I
\end{array}
\right.
\end{equation}

Dirac delta function is also constrained to satisfy the identity.

\begin{equation}\label{equ3}
\int_{SE(3)}\delta{(H)}dH=1
\end{equation}

A shifted Dirac delta function can be defined as $\delta_{A}(H)=\delta{(A^{-1}H)}$. Given two functions $f_{1}(g)$ and $f_{2}(g)$, their convolution in Lie group is defined as follows,

\begin{equation}\label{equ4}
(f_{1}\ast f_{2})(g)=\int_{SE(3)}f_{1}(h)f_{2}(h^{-1}\circ g)dh
\end{equation}

Considering the properties of $\delta$ function, the following equation is built.

\begin{equation}\label{equ5}
(f\ast \delta)(g)=\int_{SE(3)}f(h)\delta(h^{-1}\circ g)dh=f(g)
\end{equation}

Therefore, for each $A_{i}$ and $B_{i}$, we can get

\begin{IEEEeqnarray}{l}\label{equ6}
(\delta_{A_{i}}\ast \delta_{X})(g)=\delta(A_{i}^{-1} g X^{-1}) \IEEEyessubnumber
\\*
(\delta_{Y}\ast \delta_{B_{i}})(g)=\delta(Y^{-1} g B_{i}^{-1}) \IEEEyessubnumber
\end{IEEEeqnarray}

Together with $g=A_{i}X=YB_{i}$, we can obtain the convolution equation

\begin{equation}\label{equ7}
(\delta_{A_{i}}\ast \delta_{X})(g)=(\delta_{Y}\ast \delta_{B_{i}})(g)
\end{equation}

Convolution provides a linear operation on functions with additional properties. We can add up $n$ instances into a single function.

\begin{IEEEeqnarray}{l}\label{equ8}
f_{A}(g)=\frac{1}{n}\sum_{i=1}^{n} \delta(A_{i}^{-1}g) \IEEEyessubnumber
\\*
f_{B}(g)=\frac{1}{n}\sum_{i=1}^{n} \delta(B_{i}^{-1}g) \IEEEyessubnumber
\end{IEEEeqnarray}

Therefore,

\begin{equation}\label{equ9}
(f_{A_{i}}\ast \delta_{X})(g)=(\delta_{Y}\ast f_{B_{i}})(g)
\end{equation}

In each transformation set $A_i$s and $B_i$s, we are using small relative motions between consecutive reference frames. Given a measure of distance between reference frames, e.g.

\begin{eqnarray}\label{equ10}
d^{2}(A_{i},A_{j})=\parallel \Delta A \parallel_{W}^{2} = trace[(\Delta A)W(\Delta A)^{T}] = \epsilon,\nonumber \\
\end{eqnarray}

we have that  $\Delta A = A_{i}-A_{j}$ and $0 < \epsilon \ll 1 $

The convolution of "highly focused" distributions corresponding to closely clumped sets of reference frames have some interesting properties that we can exploit to solve for $X$. In particular, let the mean and covariance of a probability density, $f(g)$(e.g. $f_{A}(g),f_{B}(g)$), be defined by the conditions.

\begin{IEEEeqnarray}{l}\label{equ11}
\int_{SE(3)}log(M^{-1}g))f(g)dg=0 \IEEEyessubnumber
\\*
\Sigma = \int_{SE(3)}log^{\vee}(M^{-1}g)[log^{\vee}(M^{-1)}g)]^{T}f(g)dg \IEEEyessubnumber
\end{IEEEeqnarray}

A discrete version as for $f_{A}(g)$ is

\begin{IEEEeqnarray}{l}\label{equ12}
\sum_{i=1}^{n}log(M^{-1}g))=0 \IEEEyessubnumber
\\*
\Sigma_{A} = \sum_{i=1}^{n}log^{\vee}(M^{-1}g)[log^{\vee}(M^{-1)}g)]^{T} \IEEEyessubnumber
\end{IEEEeqnarray}

@@

An initial estimate of the iterative procedure can be $^{0}M_{A}=\frac{1}{n}\sum_{i=1}^{n}log(A_{i})$, then the process iterates until the cost function, $\parallel \sum_{i=1}^{n}log(M_{A}^{-1}A_{i}) \parallel^{2}$ falls below a predefined threshold, where the cost function is minimized and the minimum defines $M_{A}$. A similar procedure is used for computing $M_B$.

@@

Because $X$ and $Y$ is fixed, as for $\delta_{X}(g)$ and $\delta_{Y}(g)$, mean and covariance are $M_{X}=X$, $\Sigma_{X}=0$ and $M_{Y}=Y$, $\Sigma_{Y}=0$, respectively, therefore we can obtain

@@

The first blocks (\ref{equ17a}) is eigendecomposed with the same diagonal matrix due to matrix similarity $\Sigma_{M_{A}}^{1}=Q_{M_{A}}\wedge Q_{M_{A}}^{T}$, $\Sigma_{M_{B}}^{1}=Q_{M_{B}}\wedge Q_{M_{B}}^{T}$. Then,

@@

In $P=Q_{M_{A}}^{T}R_{X}Q_{M_{B}}$, $Q_{M_{A}}$ and $Q_{M_{B}}$ are constrained to be a rotation matrix and therefore $P \in \Omega \bigcup (-\Omega)$,

@@

Therefore, there are eight possibilities of $R_{X}, R_{X}=Q_{M_{A}}PQ_{M_{B}}^T$. Then, from \ref{equ17b}, eight $t_{X}$ corresponding to $R_{X}$ can be directly found. Furthermore, eight candidate $R_{Y} and t_{Y}$ can be found. At last, there are eight possibilities of solution $(X_{i},Y_{i}), i = 1,\dots,8$.
where,

@@

$AX=YB$ can be written as $AX=X(X^{-1}YB)$ and let $B' = X^{-1}YB$ . In the form $AX=XB'$, there exit two Euclidean-Group invariant relationships for one of eight groups of $(A_{i},B_{i}^k)( i = 1,\cdots,n; k=1,\dots,8), B_i^{k} = X^{-1}YB_i$ as follows,

@@

From among the four pairs $(X_{i},Y_{i})$, we can find a correct solution to minimize the absolute deviations,

@@

In most cases, the homogeneous transformations with $As$ and $Bs$ are given based on the data from different sensors. Due to asynchronous timing of the measurement transmissions, the correspondences between $A_{i}$ and $B_{i}^{k}$ is unknown. The advantage of the above probabilistic solution lies on that $X$ and $Y$ can be calculated even if without any a priori knowledge of the correspondence. However, there are still eight possible candidate results $(X_{i},Y_{i})$. Using Euclidean-Group invariants, it is straightforward to determine which pair is the correct one if the correspondence between $A_{i}$ and $B_{i}^{k}$ can be known.

The Discrete Fourier Transform (DFT) decomposes a time-domain signal into its constituent frequencies. The input is a finite list of equally spaced samples of a function. Given a discrete signal consisting of a sequence of $N$ complex numbers $x_{0},x_{1},\cdots,x_{N-1}$, the DFT is denoted by $X_{\kappa} = \mathcal{F}{x_{n}}$

\begin{equation}\label{equ21}
    X_{\kappa} = \sum_{n=0}^{N-1}x_{n}\cdot exp(-i\frac{2\pi}{N}n\kappa)
\end{equation}
The Inverse Discrete Fourier transform (IDFT) denoted by

\begin{equation}\label{equ22}
    x_{n} = \frac{1}{N}\sum_{n=0}^{N-1}X_{\kappa}\cdot exp(i\frac{2\pi}{N}n\kappa)
\end{equation}

@@

Therefore, the correspondence between the two sequences can be found. The data of $\theta_{A_{i}}$ or $d_{A_{i}}$ are shifted by $-\tau_{shift}$ to obtain a sequence of new pairs $(\theta_{A_{i}}(i+\tau_{shift}),\theta_{B_{i}^{k}})$ and $(d_{A_{i}}(i+\tau_{shift}),d_{B_{i}^{k}})$, $max(i,i+\tau_{shift})\leq i \leq min(i,i+\tau_{shift})$. The data stream can be shifted to reach correspondence once the shift is found and the correct solution can also be found by minimizing the absolute deviations based on Euclidean-Group invariants relations using the method in Section \ref{sect2}.

@@

\begin{center}
\begin{figure}
\centering
\includegraphics[width=2.6in]{fig3.eps}
\caption{
$Bs$ are randomly generated using  $B_i=B_{init}exp(\widehat{\mathbf{x}})$,$\mathbf{x}=(x_1,\dots,x_6)^T $ \ $x_i \sim \mathcal{N}(0,0.1)$.
}
\label{fig2}
\end{figure}
\end{center}

\begin{figure}
\centering
\includegraphics[width=2.6in,bb=84 202 501 581]{fig2.eps}
\caption{
$As$ are calculated using $AX=YB$. $X$ and $Y$ are assumed.
}
\label{fig3}
\end{figure}

In the numerical experiments in this section, the rotational and translational error for $X$ and $Y$ are measured as  $Error(R_X) = \parallel log^{\vee} (R_{X_{Solved}}^{T}R_{X_{true}})\parallel$, $Error(t_X) = \parallel (t_{X_{Solved}}-t_{X_{true}})\parallel$, $Error(R_Y) = \parallel log^{\vee} (R_{Y_{Solved}}^{T}R_{Y_{true}})\parallel$ and $Error(t_Y) = \parallel (t_{Y_{Solved}}-t_{Y_{true}})\parallel$ respectively.

\begin{center}
\begin{figure}
\centering
\includegraphics[width=3.2in]{fig4.eps}
\caption{
The cross correlation of data streams of $(A_{i},B_{i}^{k})$ respectively.
}
\label{fig4}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\centering
\includegraphics[width=3.2in]{fig5.eps}
\caption{
Calculated rotational and translational deviation of $X$ and $Y$ solved using the data in Fig.~\ref{fig2} and Fig.~\ref{fig3}.
}
\label{fig5}
\end{figure}
\end{center}
